PeerMind

### 2016-08-12 paper.tex
Added answers.

Another question: should feedback be visible (to see how others voted before you voted)?
People go with majority.
Better for wisdom of crowds is an independent sample.
Maybe we should only allow how other voted to be seen after you voted (but you can still change the vote),
but we could then observe that and learn from this and see if this is good or bad.
Or we could just store information if you observed existing votes before you voted (you have to click a button to see them).
Maybe going with majority is also good when you want more social cohesion in the community and not so much ``optimal''
wisdom of crowds result -  you would want that people relax their positions based on how other people care.
Cohesion of the group vs. accuracy.
Maybe display only number of votes and confidence, maybe confidence direction or graph, but not average votes.

@@

\subsection{Delegation}
\todo[inline]{Max: I think delegation graph edges should point in the direction towards the person that the vote is being given to (more intuitive).}
Because not every member of the community has time or knowledge to vote all the time, each member can delegate
decisions to one or more other members of the community.
When a member does not vote themselves, information how those delegates voted is combined into a vote of
the non-voting member.
If a delegate has not voted themselves either, their vote is computed through delegation as well, recursively.

@@

\begin{displaymath}
\mathbf{v} = \left[ \begin{array}{c}
0.70 \\
0 \\
-0.4 \\
0 \\
0 \\
\end{array} \right],\quad \mathbf{x_v} = \left[ \begin{array}{c}
0.70 \\
0.54 \\
-0.40 \\
0.056 \\
0 \\
\end{array} \right]
\end{displaymath}
\todo[inline]{Max: FYI, computing who to discard from the population as ``non-voting'' is a separate computation in itself.  You need to figure out what votes can be calculated partially as a consequence of delegation, and which cannot.  Use indicator vectors denoting 1 if member has voted, else 0.}
There are few details we have to look into.
Despite delegation some votes or parts of votes can still happen to be discarded.
Members who did not vote might have not declared their delegates.
Other members could delegate to them as well, potentially propagating lack of a vote further.
In our example, member $M_4$ has not voted so their vote is discarded.
As a consequence $M_3$'s vote cannot be computed fully, which influences $M_1$'s vote as well.

@@

We pass computed votes and number of abstentions into computation of dynamic quorum to determine
a quorum and confidence, in the same manner as if members voted themselves.

>>>>

Another question: should feedback be visible (to see how others voted before you voted)?
People go with majority.
Better for wisdom of crowds is an independent sample.
Maybe we should only allow how other voted to be seen after you voted (but you can still change the vote),
but we could then observe that and learn from this and see if this is good or bad.
Or we could just store information if you observed existing votes before you voted (you have to click a button to see them).
Maybe going with majority is also good when you want more social cohesion in the community and not so much ``optimal''
wisdom of crowds result -  you would want that people relax their positions based on how other people care.
Cohesion of the group vs. accuracy.
Maybe display only number of votes and credibility, maybe credibility direction or graph, but not average votes.

@@

\subsection{Delegation}
\todo[inline]{Max: I think delegation graph edges should point in the direction towards the person that the vote is
being given to (more intuitive).
\\
Mitar: We are not giving votes to people, we are delegating a decision to people, but votes are computed for each person
separately based on how delegates voted themselves. The idea is that you ask a delegate how the voted and then compute
your vote. The do not get your vote to do anything with it. This is why arrows are like that. Maybe the word
"delegation" is confusing and we should maybe use surrogate or some other word.}
Because not every member of the community has time or knowledge to vote all the time, each member can delegate
decisions to one or more other members of the community.
When a member does not vote themselves, information how those delegates voted is combined into a vote of
the non-voting member.
If a delegate has not voted themselves either, their vote is computed through delegation as well, recursively.

@@

\begin{displaymath}
\mathbf{v} = \left[ \begin{array}{c}
0.70 \\
0 \\
-0.4 \\
0 \\
0 \\
\end{array} \right],\quad \mathbf{x_v} = \left[ \begin{array}{c}
0.70 \\
0.54 \\
-0.40 \\
0.056 \\
0 \\
\end{array} \right]
\end{displaymath}

\todo[inline]{Max: FYI, computing who to discard from the population as ``non-voting'' is a separate computation in itself.
You need to figure out what votes can be calculated partially as a consequence of delegation, and which cannot.
Use indicator vectors denoting 1 if member has voted, else 0.
\\
Mitar: This is exactly what $\mathbf{w}$ is later on.}

There are few details we have to look into.
Despite delegation some votes or parts of votes can still happen to be discarded.
Members who did not vote might have not declared their delegates.
Other members could delegate to them as well, potentially propagating lack of a vote further.
In our example, member $M_4$ has not voted so their vote is discarded.
As a consequence $M_3$'s vote cannot be computed fully, which influences $M_1$'s vote as well.

@@

We pass computed votes and number of abstentions into computation of dynamic quorum to determine
a quorum and credibility, in the same manner as if members voted themselves.
